Implementation and Analysis of Homomorphic Facial Image Encryption and Manipulation

### 2019-01-09 paper/paper-conf.tex
Results!

\subsection{Cryptosystem Implementation}

Four homomorphic encryption schemes are investigated. For cryptosystems with readily available open-source implementations, such implementations are used. For the remaining cryptosystems, the encryption and decryption methods were implemented in Python.
\begin{itemize}
	\item The Paillier cryptosystem is incorporated using the implementation at \url{https://github.com/n1analytics/python-paillier} developed by Data61 - CSIRO.
	\item The BGV cryptosystem is implemented using the Pyfhel library (\url{https://github.com/ibarrond/Pyfhel}) using a HElib backend from (\url{https://github.com/shaih/HElib}).
	\item The DGK and Dasgupta--Pal cryptosystem are implemented from scratch.
\end{itemize}

@@

Similar to the logarithm transformation, we must provide an approximation for $x^\gamma$.
We have derived an infinite series in Appendix \ref{sec:logapproximation}.
\begin{align*}
	x^\gamma &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
\end{align*}
Partial sums of the above infinite series can be calculated based on the closed form approximation for the logarithm in Equation \ref{eq:scaledquadraturech3}. For the implementation of the power-law transformation, the first six terms of the infinite series were used.

\subsection{Assessment of Homomorphic Encryption Schemes}

Lab computers in Faura Hall, Ateneo de Manila University were used to perform the computations, and processing time was tracked using built-in timing functions. The processing time for all cases were recorded.

@@

We first obtained standard test images from~\cite{gonzalez_image_nodate}. Grayscale images were used in the study.

@@

Training and test data were secured from the \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.

The facial recognition tests were done using ten-fold cross-validation for each cryptosystem, where the number of principal components used by the algorithm is fixed at $K=5$.

Prior to splitting the dataset, the images within each set are shuffled. Since there are twenty (20) images per set, two images are taken at a time for each round of cross-validation. The first round would take the first two images from each set as part of the test set, and the rest of the images will be part of the training set. Then, the succeeding round would take the next two images from each set as part of the test set, and so on until ten rounds have been done. After every round of cross-validation, the accuracy score, confusion matrix, and total processing time were obtained.

@@

\section{Preliminary Results and Discussion}
The results shown here are gathered from the tests for intensity transformations under Paillier and Dasgupta--Pal cryptosystems. During testing, the Pyfhel library being used for the BGV cryptosystem is still

\subsection{Intensity Transformations}
\begin{table}[h]
    \caption{Image negation under Paillier}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
        \texttt{anpage} & 0.000 & $\infty$ & 1.00000 & 0.084 & 0.010 & 0.016 \\
		\texttt{bplyce} & 0.000 & $\infty$ & 1.00000 & 0.063 & 0.008 & 0.016 \\
		\texttt{drbost} & 0.000 & $\infty$ & 1.00000 & 0.062 & 0.008 & 0.016 \\
		\texttt{ksunth} & 0.000 & $\infty$ & 1.00000 & 0.077 & 0.010 & 0.017 \\
		\texttt{martin} & 0.000 & $\infty$ & 1.00000 & 0.067 & 0.008 & 0.023 \\
		\texttt{pmives} & 0.000 & $\infty$ & 1.00000 & 0.060 & 0.008 & 0.016 \\
		\texttt{rnpwil} & 0.000 & $\infty$ & 1.00000 & 0.061 & 0.008 & 0.030 \\
		\texttt{sbains} & 0.000 & $\infty$ & 1.00000 & 0.061 & 0.008 & 0.033 \\
		\texttt{swewin} & 0.000 & $\infty$ & 1.00000 & 0.072 & 0.008 & 0.016 \\
		\texttt{yfhsie} & 0.000 & $\infty$ & 1.00000 & 0.062 & 0.008 & 0.016 \\
		\bottomrule
        \end{tabular}
\end{table}
\begin{table}[h]
    \caption{Logarithm transformation under Paillier}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
        \texttt{anpage} & 13.143 & 36.944 & 0.99311 & 0.073 & 1.238 & 0.016 \\
		\texttt{bplyce} & 6.870 & 39.761 & 0.99038 & 0.061 & 1.324 & 0.016 \\
		\texttt{drbost} & 8.019 & 39.089 & 0.98642 & 0.061 & 1.284 & 0.016 \\
		\texttt{ksunth} & 25.194 & 34.118 & 0.98944 & 0.065 & 1.318 & 0.042 \\
		\texttt{martin} & 10.148 & 38.067 & 0.98744 & 0.078 & 1.271 & 0.023 \\
		\texttt{pmives} & 2.404 & 44.322 & 0.99420 & 0.056 & 1.384 & 0.021 \\
		\texttt{rnpwil} & 5.087 & 41.067 & 0.98968 & 0.071 & 1.322 & 0.016 \\
		\texttt{sbains} & 16.762 & 35.888 & 0.98512 & 0.058 & 1.338 & 0.016 \\
		\texttt{swewin} & 5.686 & 40.583 & 0.99360 & 0.067 & 1.360 & 0.016 \\
		\texttt{yfhsie} & 12.135 & 37.290 & 0.99383 & 0.057 & 1.293 & 0.017 \\
		\bottomrule
        \end{tabular}
\end{table}
\begin{table}[h]
    \caption{Power-law transformation under Paillier}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
        \texttt{anpage} & 4264.991 & 11.832 & 0.35971 & 0.058 & 12.800 & 0.016 \\
		\texttt{bplyce} & 881.611 & 18.678 & 0.87174 & 0.056 & 13.017 & 0.021 \\
		\texttt{drbost} & 1166.789 & 17.461 & 0.83118 & 0.072 & 12.462 & 0.018 \\
		\texttt{ksunth} & 648.512 & 20.012 & 0.91254 & 0.071 & 12.667 & 0.037 \\
		\texttt{martin} & 541.318 & 20.796 & 0.90277 & 0.069 & 12.515 & 0.018 \\
		\texttt{pmives} & 1933.216 & 15.268 & 0.65838 & 0.060 & 12.957 & 0.016 \\
		\texttt{rnpwil} & 728.828 & 19.505 & 0.87270 & 0.064 & 13.752 & 0.016 \\
		\texttt{sbains} & 617.591 & 20.224 & 0.91169 & 0.079 & 12.578 & 0.016 \\
		\texttt{swewin} & 7985.854 & 9.108 & 0.45367 & 0.074 & 12.884 & 0.016 \\
		\texttt{yfhsie} & 2114.705 & 14.878 & 0.60351 & 0.076 & 13.625 & 0.016 \\
		\bottomrule
        \end{tabular}
\end{table}
\begin{table}[h]
    \caption{Image negation under Dasgupta--Pal}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
		\texttt{anpage} & 0.000 & $\infty$ & 1.00000 & 0.150 & 22.523 & 0.152 \\
		\texttt{bplyce} & 0.000 & $\infty$ & 1.00000 & 0.258 & 21.940 & 0.265 \\
		\texttt{drbost} & 0.000 & $\infty$ & 1.00000 & 0.172 & 22.164 & 0.207 \\
		\texttt{ksunth} & 0.000 & $\infty$ & 1.00000 & 0.222 & 20.952 & 0.156 \\
		\texttt{martin} & 0.000 & $\infty$ & 1.00000 & 0.145 & 28.285 & 0.181 \\
		\texttt{pmives} & 0.000 & $\infty$ & 1.00000 & 0.181 & 21.873 & 0.169 \\
		\texttt{rnpwil} & 0.000 & $\infty$ & 1.00000 & 0.175 & 22.408 & 0.235 \\
		\texttt{sbains} & 0.000 & $\infty$ & 1.00000 & 0.158 & 22.312 & 0.273 \\
		\texttt{swewin} & 0.000 & $\infty$ & 1.00000 & 0.255 & 27.705 & 0.225 \\
		\texttt{yfhsie} & 0.000 & $\infty$ & 1.00000 & 0.289 & 26.008 & 0.185 \\		
		\bottomrule
        \end{tabular}
\end{table}

>>>>

\subsection{Cryptosystem Implementation}
Four homomorphic encryption schemes are investigated. For cryptosystems with readily available open-source implementations, such implementations are used. For the remaining cryptosystems, the encryption and decryption methods were implemented in Python.
\begin{itemize}
	\item The Paillier cryptosystem is incorporated using the implementation at \url{https://github.com/n1analytics/python-paillier} developed by Data61 - CSIRO.
	\item The BGV cryptosystem is implemented using the Pyfhel library (\url{https://github.com/ibarrond/Pyfhel}) using a HElib backend from (\url{https://github.com/shaih/HElib}).
	\item The DGK and Dasgupta--Pal cryptosystems are implemented from scratch with Python.
\end{itemize}

@@

Similar to the logarithm transformation, we must provide an approximation for $x^\gamma$.
We have derived an infinite series in Appendix \ref{sec:logapproximation}.
\begin{align*}
	x^\gamma &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
\end{align*}
Partial sums of the above infinite series can be calculated based on the closed form approximation for the logarithm in Equation \ref{eq:scaledquadraturech3}. For the implementation of the power-law transformation, a partial sum consisting of the first five terms of the infinite series were used.

\subsection{Assessment of Homomorphic Encryption Schemes}
A laptop computer with a 2.5 GHz Intel Core i7 quad-core processor and 8 GB of RAM is used to perform the computations, and processing time was tracked using built-in timing functions. The processing time for all cases were recorded. All of the tests are done using Python 3.7.1 running under Linux.

@@

We first obtained test images from the \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex. However, only ten distinct facial images from the dataset were selected for the purposes of this test. Since only grayscale images are used in the study, the images were converted to grayscale and then downsampled to $40 \times 36$ pixels.

@@

As before, training and test data were also secured from the \texttt{faces94} dataset. The images were first converted to grayscale but it is not downsampled, unlike in the previous test.

The facial recognition tests are done using ten-fold cross-validation for each cryptosystem, where the number of principal components used by the algorithm is fixed at $K=5$.

Prior to splitting the dataset, the images within each set are shuffled. Since there are twenty (20) images per set, two images are taken at a time for each round of cross-validation. The first round would take the first two images from each set as part of the test set, and the rest of the images will be part of the training set. Then, the succeeding round would take the next two images from each set as part of the test set, and so on until ten rounds have been done. After every round of cross-validation, the accuracy score, confusion matrix, and total processing time are obtained.

@@

\section{Preliminary Results and Discussion}
The results shown in this section are gathered from the tests for intensity transformations under Paillier and Dasgupta--Pal cryptosystems. During testing, initial results obtained from BGV, particularly with image operations involving floating-point numbers like the logarithmic transformation, were unstable (i.e. the results vary drastically every time the same tests were done). This is because the Pyfhel library being used for the BGV cryptosystem is still in alpha development stage \cite{pyfhel_2018}.

% One of the authors has already informed the maintainers of the library about a bug involving exponentiation of two real numbers.

\subsection{Intensity Transformations}
The following tables show the resulting metric scores for mean squared error (MSE), peak signal to noise ratio (PSNR), and structural similarity index (SSIM), as well as time taken for encrypting the input image ($t_\text{enc}$), applying an operation to the encrypted image ($t_\text{apply}$), and decrypting the resulting encrypted image ($t_\text{dec}$), for each image in the test set.

\subsubsection{Image Negation}
Both the Paillier and Dasgupta--Pal cryptosystems were able to perform image negation under the encrypted domain without introducing noise in the resulting image. In other words, the resulting image from doing image negation on an image on the clear and doing image negation under the encrypted domain are identical, as evidenced by the mean squared errors being exactly equal to zero and the SSIM being exactly equal to one.

The Paillier cryptosystem performed better in terms of time, only taking about 0.01 seconds to apply image negation. On the other hand, the Dasgupta--Pal cryptosystem took about 22 seconds each to apply the same operation, which is expected since the implementation for Dasgupta--Pal was done in Python without using any external libraries.

\begin{table}[!h]
    \caption{Image negation under Paillier}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
        \texttt{anpage} & 0.000 & inf & 1.00000 & 0.128 & 0.013 & 0.041 \\
		\texttt{bplyce} & 0.000 & inf & 1.00000 & 0.084 & 0.013 & 0.024 \\
		\texttt{drbost} & 0.000 & inf & 1.00000 & 0.099 & 0.012 & 0.031 \\
		\texttt{ksunth} & 0.000 & inf & 1.00000 & 0.109 & 0.012 & 0.048 \\
		\texttt{martin} & 0.000 & inf & 1.00000 & 0.117 & 0.015 & 0.043 \\
		\texttt{pmives} & 0.000 & inf & 1.00000 & 0.111 & 0.012 & 0.025 \\
		\texttt{rnpwil} & 0.000 & inf & 1.00000 & 0.099 & 0.012 & 0.023 \\
		\texttt{sbains} & 0.000 & inf & 1.00000 & 0.084 & 0.012 & 0.024 \\
		\texttt{swewin} & 0.000 & inf & 1.00000 & 0.089 & 0.012 & 0.023 \\
		\texttt{yfhsie} & 0.000 & inf & 1.00000 & 0.081 & 0.012 & 0.029 \\
		\bottomrule
        \end{tabular}
\end{table}
\begin{table}[!h]
    \caption{Image negation under Dasgupta--Pal}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
		\texttt{anpage} & 0.000 & inf & 1.00000 & 0.221 & 30.217 & 0.239 \\
		\texttt{bplyce} & 0.000 & inf & 1.00000 & 0.190 & 30.919 & 0.216 \\
		\texttt{drbost} & 0.000 & inf & 1.00000 & 0.284 & 31.182 & 0.268 \\
		\texttt{ksunth} & 0.000 & inf & 1.00000 & 0.225 & 32.581 & 0.223 \\
		\texttt{martin} & 0.000 & inf & 1.00000 & 0.220 & 32.220 & 0.271 \\
		\texttt{pmives} & 0.000 & inf & 1.00000 & 0.287 & 31.224 & 0.294 \\
		\texttt{rnpwil} & 0.000 & inf & 1.00000 & 0.285 & 29.478 & 0.284 \\
		\texttt{sbains} & 0.000 & inf & 1.00000 & 0.186 & 29.784 & 0.362 \\
		\texttt{swewin} & 0.000 & inf & 1.00000 & 0.243 & 38.407 & 0.220 \\
		\texttt{yfhsie} & 0.000 & inf & 1.00000 & 0.285 & 29.488 & 0.449 \\		
		\bottomrule
        \end{tabular}
\end{table}

\subsubsection{Logarithm Transformation}
\begin{table}[!h]
    \caption{Logarithm transformation under Paillier}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
		\texttt{anpage} & 13.369 & 36.870 & 0.99263 & 0.085 & 1.813 & 0.023 \\
		\texttt{bplyce} & 7.072 & 39.635 & 0.99017 & 0.089 & 2.073 & 0.023 \\
		\texttt{drbost} & 8.151 & 39.019 & 0.98688 & 0.091 & 1.913 & 0.023 \\
		\texttt{ksunth} & 25.253 & 34.108 & 0.98927 & 0.089 & 1.919 & 0.023 \\
		\texttt{martin} & 10.374 & 37.971 & 0.98695 & 0.106 & 1.829 & 0.023 \\
		\texttt{pmives} & 2.426 & 44.283 & 0.99401 & 0.127 & 1.900 & 0.023 \\
		\texttt{rnpwil} & 5.184 & 40.985 & 0.98971 & 0.096 & 1.853 & 0.023 \\
		\texttt{sbains} & 16.772 & 35.885 & 0.98492 & 0.081 & 1.746 & 0.024 \\
		\texttt{swewin} & 5.803 & 40.494 & 0.99241 & 0.091 & 1.827 & 0.027 \\
		\texttt{yfhsie} & 12.192 & 37.270 & 0.99354 & 0.081 & 1.815 & 0.023 \\
		\bottomrule
        \end{tabular}
\end{table}
\begin{table}[!h]
    \caption{Logarithm transformation under Dasgupta--Pal}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
		\texttt{anpage} & 0.004 & 71.624 & 0.99999 & 0.287 & 802.957 & 0.036 \\
		\texttt{bplyce} & 0.000 & 82.043 & 1.00000 & 0.190 & 815.384 & 0.048 \\
		\texttt{drbost} & 0.004 & 72.480 & 1.00000 & 0.270 & 813.640 & 0.036 \\
		\texttt{ksunth} & 0.000 & 87.372 & 1.00000 & 0.204 & 804.629 & 0.047 \\
		\texttt{martin} & 0.001 & 77.421 & 1.00000 & 0.245 & 822.940 & 0.036 \\
		\texttt{pmives} & 0.001 & 76.934 & 1.00000 & 0.194 & 814.132 & 0.036 \\
		\texttt{rnpwil} & 0.000 & 83.135 & 1.00000 & 0.197 & 808.503 & 0.047 \\
		\texttt{sbains} & 0.001 & 77.301 & 1.00000 & 0.270 & 809.406 & 0.047 \\
		\texttt{swewin} & 0.006 & 70.004 & 0.99999 & 0.268 & 813.217 & 0.051 \\
		\texttt{yfhsie} & 0.001 & 78.576 & 1.00000 & 0.243 & 830.640 & 0.039 \\
		\bottomrule
        \end{tabular}
\end{table}

\subsubsection{Power-Law Transformation}
\begin{table}[!h]
    \caption{Power-law transformation under Paillier}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
        \texttt{anpage} & 3910.678 & 12.208 & 0.46712 & 0.099 & 14.695 & 0.024 \\
		\texttt{bplyce} & 873.064 & 18.720 & 0.84379 & 0.139 & 16.190 & 0.023 \\
		\texttt{drbost} & 1261.059 & 17.123 & 0.77229 & 0.082 & 13.866 & 0.023 \\
		\texttt{ksunth} & 653.049 & 19.981 & 0.90673 & 0.083 & 15.507 & 0.023 \\
		\texttt{martin} & 646.310 & 20.026 & 0.88157 & 0.108 & 15.727 & 0.045 \\
		\texttt{pmives} & 2047.933 & 15.018 & 0.69408 & 0.113 & 14.728 & 0.034 \\
		\texttt{rnpwil} & 806.473 & 19.065 & 0.85346 & 0.082 & 14.253 & 0.024 \\
		\texttt{sbains} & 616.419 & 20.232 & 0.92334 & 0.121 & 14.415 & 0.023 \\
		\texttt{swewin} & 8270.696 & 8.955 & 0.43185 & 0.112 & 14.362 & 0.065 \\
		\texttt{yfhsie} & 1715.478 & 15.787 & 0.73857 & 0.145 & 20.239 & 0.023 \\
		\bottomrule
        \end{tabular}
\end{table}
